\documentclass[letterpaper, 10pt,colorlinks,linkcolor=cyan]{moderncv}
  \usepackage{lmodern}
  \usepackage[english]{babel}
  \usepackage{courier}
  \hyphenpenalty=100000
  \hbadness=99999
%% Themes
  \moderncvstyle{casual}
  \moderncvcolor{red}
  \nopagenumbers{}
%% Encoding
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
%% Margins
  \usepackage[scale=0.85]{geometry}
  \setlength{\hintscolumnwidth}{2.81cm}
%% Data
  \firstname{\textsc{Daniel}}
  \familyname{\textsc{Hardesty Lewis}}
  \address{\textsc{155~Claremont~Ave}}{\textsc{New~York,~NY~10027}}{\textsc{United~States}}
  \phone[mobile]{+1~(713)~371-7875}
  \email{daniel@summitgeospatial.com}
  % \homepage{tacc.utexas.edu/about/directory/daniel-lewis}
  \social[linkedin]{dhardestylewis}
  \social[github]{dhardestylewis}
  \social[gitlab]{dhl}
  \extrainfo{\url{researchgate.net/profile/Daniel-Hardesty-Lewis}}
%% Define \cvdoublecolumn
  \newcommand{\cvdoublecolumn}[2]{
    \cvitem[0.75em]{}{
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
      \hfill
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
  }

\begin{document}
  \definecolor{links}{HTML}{0645AD}
  \hypersetup{urlcolor=links}
  \makecvtitle

  \section{\textsc{Education}}
    \cventry{expected 2026}{M.S., Urban Planning}{Columbia University}{New York City,~NY}{}{}
    \cventry{2017}{B.S., Pure Mathematics}{University of Texas}{Austin,~TX}{}{}
    \cventry{2017}{Certificate, Scientific~Computation}{University of Texas}{Austin,~TX}{}{}
  
  \section{\textsc{Experience}}
  \subsection{\textsc{Professional}}
    \cventry{Apr. 2025 -- Present}{Co-founder}{Properlytic}{New York, NY}{}{
    Targetting the last blue ocean in consumer real estate technology: individual home price forecasting
    \begin{itemize}
        \item Here's our \href{https://docs.google.com/presentation/d/1HL2zPTLxuGdq9k12Z6J_RQA4Dt64ZKEsSVrTQpbQuNA/edit?usp=sharing}{pitch}
        \item Built out a current home price prediction ML model, achieving 12\% MAPE against Zillow's 8.4\% in the hardest US market to do it: Manhattan
        \item That model stack is identical to some of the recent cutting-edge physics foundation models, using a Variational AutoEncoder (VAE) approach
        \item Uses a data-driven approach to auto-configure the vast majority of hyperparameters and even some of the model architecture, trains in under 7 min
        \item Interest from a16z \& MetaProp
     \end{itemize}}

    \cventry{Nov. 2024 -- Present}{Co-founder}{PoliBOM}{Seattle, WA}{}{
    Top-5\% YC entrant, KPMG rolled out their \href{https://kpmg.com/us/en/capabilities-services/tax-services/international-tax-trade-and-transfer-pricing/trade-customs/kpmg-tariff-modeler.html}{Tariff Modeller} after we put \href{https://polibom.com}{polibom.com} in front of them
    \begin{itemize}
        \item Now targetting early stage investment
    \end{itemize}}

    \cventry{Nov. 2023 -- Present}{Founder}{Summit Geospatial}{New York, NY}{}{
    Developed the highest quality seamless elevation data for Texas, \href{https://summitgeospatial.com}{summitgeospatial.com}
    \begin{itemize}
        \item Now targetting recent interest received to license to AI labs such as OpenAI \& Cohere
    \end{itemize}}

    \cventry{Aug. 2021 -- Aug. 2023}{Senior Data Scientist \& Technical Lead}{Texas Advanced Computing Center (TACC)}{Austin, TX}{}{
    \begin{itemize}
        \item Spun out Summit Geospatial alongside UT's VPs of IP
        \item Led a principal project of the \$40M Texas Disaster Information System (TDIS) disaster resiliency initiative
        \item Contributed research towards Paola Passalacqua's 2022 EGU Bagnold Medal, one of geomorphology's highest honors
        \item Scaled climate and flood models on world-leading supercomputers, utilizing millions of dollars in computational resources and million-node jobs
        \item Evaluated and accepted tens of millions of dollars in compute requests
        \item Managed relationships and developed projects with federal, state agencies, and universities including NOAA, NSF, US Army Corps of Engineers, Texas General Land Office, USC, UT, A\&M
    \end{itemize}}
    
    \cventry{Feb. 2018 -- Jul. 2021}{Data Scientist \& Research Engineer}{Texas Advanced Computing Center (TACC)}{Austin, TX}{}{
    \begin{itemize}
        \item Competed in DARPA World Modelers program, focusing on disaster resiliency in East Africa
        \item Research received a mention from President of AAAI Yolanda Gil during her farewell speech
        \item Helped teach Petrobras deep learning on HPC
    \end{itemize}}

  \subsection{\textsc{Research}}

    \cventry{May 2025 -- Present}{Research assistant to Dir. Electrical Engineering Zoran Kostic}{Columbia University}{New York, NY}{}{Targetting theory publications to DeepSeek's GRPO algorithm}

    \cventry{Jan. 2025 -- Present}{Research assistant to Dir. Financial Engineering Ali Hirsa}{Columbia University}{New York, NY}{}{Achieved better than  \href{https://www.arcana.io/}{commercial \(R^2\)} on backtested holdout prediction of daily mutual fund returns on a variety of asset classes
    \begin{itemize}
        \item Using a DL latent factor model to produce better factors than our benchmark: Fama-French's 5-factor model
        \item Now targetting SHAP explainability publication
    \end{itemize}}
    
    \cventry{July 2019 -- Aug. 2019}{Summer research intern to Pres. AAAI Yolanda Gil}{University of Southern California}{Los Angeles, CA}{}{Integrated hydrological models into team's DARPA-supported scientific model orchestration portal}

  \subsection{\textsc{Teaching}}

    \cventry{Jan. 2018 -- Dec. 2020}{Co-instructor}{The University of Texas at Austin}{Austin, TX}{}{Helped teach graduate-level courses: \emph{Machine Learning for the Geosciences}, \emph{Intelligent Systems for the Geosciences}, and \emph{Scientific Computation}, including C++, CUDA, HPC, \& optimization}

  \section{\textsc{Key Projects}}
    \cvitem{oppsAlert}{Developed the first property- and owner-level ML model of NIMBYism, using 15+ years of 15000+ points of individual homeowner protest data provided by the City of Austin}
    \cvitem{Stealth, RegTech}{\textit{Seeking PE investment:} Teaming up with a top-proptech operator for a very large opportunity to aid cities achieve permitting compliance via simple pipeline collating publicly available imagery against permitting data}
    \cvitem{Flood Hazard Assessment}{Partnered with the US Army Corps of Engineers to statistically model compound flood hazards in coastal Texas, integrating high-resolution topographic data with hydrological models.}
    \cvitem{Texas Disaster Information System (\textsc{TDIS})}{Led development of the core elevation data layer for a web-based spatial data system that supports resilient decision-making at the state and local levels.}
    \cvitem{Real-Time Inundation Mapping}{Developed computationally efficient methods to produce high-resolution (1m) flood inundation maps from National Water Model outputs for emergency response personnel.}

  \section{\textsc{Technology Skills}}
    \cvdoubleitem{Programming Languages}{\raggedright Python, Bash, PL/pgSQL, Fortran, Perl, C++}{Operating Systems}{\raggedright \textsc{gnu}/Linux, mac\textsc{os}, Windows}
    \cvdoubleitem{Libraries \& Frameworks}{\raggedright \textsc{gdal}, \textsc{cuda}, GeoPandas, RasterIO, NumPy, Plotly, Dash}{Database Systems}{\raggedright PostgreSQL, Redis, Supabase, PostGIS}
    \cvdoubleitem{Scientific Software}{\raggedright \textsc{modflow}, \textsc{hand}, \textsc{hec-ras}, \textsc{mesa}}{Cloud \& Virtualization}{\raggedright AWS, Azure, Docker, Singularity}
    \cvdoubleitem{AI tooling}{\raggedright ChatGPT, Claude, Gemini, VSCode, v0.dev}{ML}{\raggedright \textsc{vae}, Tree-based models}
    \cvdoubleitem{Clustering techniques \& metrics}{\raggedright \textsc{dbscan}, Hierarchical, Silhouette score, Calinski-Harabasz, Davies-Bouldin}{Statistical \& ML metrics}{\raggedright 
     \(R^2\), \textsc{mape}, \textsc{rmse}, KL-div, Reconstruction loss}

  \section{\textsc{Peer-reviewed~articles}}
    \cvitem{2021~July}{Gil,~Y., D.~Garijo, D.~Khider, C.~A.~Knoblock, M.~Osorio, H.~Vargas, M.~Pham, J.~Pujara, B.~Shbita, B.~Vu, Y.~Chiang, D.~Feldman, Y.~Lin, H.~Song, V.~Kumar, A.~Khandelwal, M.~Steinbach, K.~Tayal, S.~Xu, S.~A.~Pierce, L.~Pearson, \emph{D.~Hardesty~Lewis}, E.~Deelman, R.~F.~da~Silva, R.~Mayani, A.~R.~Kemanian, Y.~Shi, L.~Leonard, S.~.D.~Peckham, M.~Stoica, K.~M.~Cobourn, Z.~Zhang, C.~Duffy, L.~Shu. "Artificial Intelligence for Modeling Complex Systems: Taming the Complexity of Expert Models to Improve Decision Making". {\small The ACM Transactions on Interactive Intelligent Systems 11(2):11.}}
  \section{\textsc{Conference~papers}}
    \cvitem{2019~Mar.}{Garijo,~D., J.~Pujara, B.~Vu, D.~Feldman, R.~Mayani, K.~Cobourn, C.~Duffy, A.~R.~Kemanian, L.~Shu, V.~Kumar, A.~Khandelwal, D.~Khider, K.~Tayal, S.~D.~Peckham, M.~Stoica, A.~Dabrowski, \emph{D.~Hardesty~Lewis}, S.~A.~Pierce, V.~Ratnakar, Y.~Gil, E.~Deelman, R.~F.~da~Silva, C.~Knoblock, Y.~Chiang, M.~Pham. "An intelligent interface for integrating climate, hydrology, agriculture, and socioeconomic models". {\small ACM 24th International Conference on Intelligent User Interfaces (IUI'19).}}
    \cvitem{2018~June}{Garijo,~D., D.~Khider, Y.~Gil, L.~A.~M.~C.~Carvalho, B.~T.~Essawy, S.~A.~Pierce, \emph{D.~Hardesty~Lewis}, V.~Ratnakar, S.~D.~Peckham, C.~Duffy, J.~L.~Goodall. "A Semantic Model Catalog to Support Comparison and Reuse". {\small 9th International Congress on Environmental Modelling and Software.}}
  \section{\textsc{Technical~reports}}
    \cvitem{2021~Mar.}{Sun,~A., M.~H.~Young, S.~A.~Pierce, J.~Thompson, \emph{D.~Hardesty~Lewis}, B.~R.~Scanlon. "Development of a Framework of Data Interpolation, Scaling, and Homogenization (DISH) for Mapping Natural Resources and Socioeconomic Data in Texas".}
    \cvitem{2019~Oct.}{Khider,~D., Y.~Gil, D.~Garijo, K.~M.~Cobourn, C.~Duffy, A.~R.~Kemanian, S.~D.~Peckham, B.~Watkins, A.~Campion, C.~Preager, S.~A.~Pierce, \emph{D.~Hardesty~Lewis}, A.~Dabrowski, C.~H.~Porter, M.~Landsfeld, M.~Puma, B.~Schauberger, A.~Sliva, C.~T.~Morrison. "Towards a Shared Modeling Terminology and Problem Specification Framework".}
  \section{\textsc{Presentations}}
    \cvitem{2021~May}{Passalacqua,~P., F.~R.~Salas, R.~Schomp, A.~Carruthers, \emph{D.~Hardesty~Lewis}. "Estimating Inundation Extent and Depth from National Water Model Outputs and High Resolution Topographic Data". {\small Presented to the National Oceanographic and Atmospheric Administration.}}
    \cvitem{2020~Dec.}{Sun,~A., J.~Thompson, \emph{D.~Hardesty~Lewis}, J.~Powell, M.~H.~Young, B.~R.~Scanlon, S.~A.~Pierce. "Development of a Framework of Data Interpolation, Scaling, and Homogenization (DISH) for Mapping Natural Resources in Texas". {\small Presented at the 2020 annual Fall Research Showcase of Planet Texas 2050.}}
    \cvitem{2020~Sep.}{Passalacqua,~P., D.~R.~Maidment, D.~Arctur, H.~Evans, C.~Thies, A.~Carruthers, R.~Schomp, \emph{D.~Hardesty~Lewis}, S.~A.~Pierce. "From Rain Forecasts to Stream Flow to Flood Modelling". {\small Presented at the 2020 annual Fall Research Showcase of Planet Texas 2050.}}
    \cvitem{2020~Aug.}{\emph{Hardesty~Lewis,~D.}. "Vector and Raster GIS Processing with Python in Jupyter Notebooks". {\small Presented at the 2020 annual TACC Institute of Planet Texas 2050.}}
    \cvitem{2019~Sep.}{\emph{Hardesty~Lewis,~D.}, A.~Dabrowski, J.~Powell, S.~A.~Pierce. "DataX and MINT Overview". {\small Presented at the 2019 annual Fall Research Showcase of Planet Texas 2050.}}
  \section{\textsc{Posters}}
    \cvitem{2019~Dec.}{Khider,~D., Y.~Gil, K.~M.~Cobourn, E.~Deelman, C.~Duffy, R.~F.~da~Silva, A.~R.~Kemanian, C.~A.~Knoblock, V.~Kumar, S.~D.~Peckham, Y.~Chiang, D.~Feldman, D.~Garijo, \emph{D.~Hardesty~Lewis}, A.~Khandelwal, R.~Mayani, M.~Osorio, M.~Pham, S.~A.~Pierce, J.~Pujara, V.~Ratnakar, L.~Shu, H.~J.~Song, B.~Shbita, M.~Stoica, B.~Vu, L.~Pearson. "MINT: An intelligent interface for understanding the impacts of climate change on hydrological, agricultural and economic systems". {\small Poster presented at the 2019 annual fall meeting of the American Geophysical Union.}}
    \cvitem{2019~June}{\emph{Hardesty~Lewis,~D.}, J.~C.Thompson, E.~Pease, Q.~Yang, M.~H.~Young, S.~A.~Pierce. "A unified data representation of Texas water resources". {\small Poster presented at the 2019 annual meeting of the Earthcube community.}}
    \cvitem{2019~June}{Pierce,~S.~A., J.~Powell, A.~Karpatne, D.~Garijo, J.~Martin, \emph{D.~Hardesty~Lewis}, P.~Marchetto, S.~Cleveland, M.~Daniels, I.~Athanasiadis, P.~Keys, I.~Demir, D.~Fuka, S.~Peckham, M.~Hill, I.~Ebert-Uphoff, D.~Pennington, G.~Jacobs, Y.~Gil. "Intelligent Systems and Geosciences". {\small Poster presented at the 2019 annual meeting of the Earthcube community.}}
    \cvitem{2019~June}{Powell~J., A.~Karpatne, D.~Garijo, J.~Martin, \emph{D.~Hardesty~Lewis}, P.~Marchetto, S.~Cleveland, M.~Daniels, I.~N.~Athanasiadis, P.~W.~Keys, I.~Demir, S.~D.~Peckham, M.~Hill, I.~Ebert-Uphoff, D.~Pennington, G.~Jacobs, Y.~Gil, S.~A.~Pierce. "Creating Sustainable Knowledge Centric Communities with Artificial Intelligence Applications to Earth Science Problems". {\small Poster presented at the 2019 annual meeting of the Earthcube community.}}
    \cvitem{2019~June}{Pease,~E., J.~C.~Thompson, \emph{D.~Hardesty~Lewis}, Q.~Yang, S.~A.~Pierce, M.~H.~Young. "Integrated Modeling of Texas Water Resources". {\small Poster presented at the 2019 annual meeting of the \textsc{modflow} and More conference series.}}
    \cvitem{2018~Dec.}{Pease,~E., A.~Pfeil, V.~Ibarra, S.~Siddique, F.~Apango, O.~Ramirez, E.~Collado, \emph{D.~Hardesty~Lewis}, N.~Freed, S.~A.~Pierce. "Groundwater Modeling with Informatics and Automated Workflows for Water Resource Management: A Case Study from the Northern Trinity Aquifer". {\small Poster presented at the 2018 annual fall meeting of the American Geophysicial Union.}}
    \cvitem{2018~Sep.}{Martin,~J., \emph{D.~Hardesty~Lewis}, N.~Freed, S.~A.~Pierce. "The IS-GEO Gateway: A community portal to facilitate AI and knowledge centered earth discoveries". {\small Poster presented at the 13\textsuperscript{th} annual conference of Gateway Computing Environments.}}
    \cvitem{2018~June}{Martin,~J., D.~Garijo, N.~Freed, S.~A.~Pierce, Y.~Gil, D.~R.~Thompson, I.~Demir, I.~Ebert-Uphoff, D.~Pennington, \emph{D.~Hardesty~Lewis}, M.~Hill, D.~Fuka. "IS-GEO: A Research Coordination Network on Intelligent Systems Research to Support he Geosciences". {\small Poster presented at the 2018 annual meeting of the EarthCube community.}}
    \cvitem{2017~Dec.}{\emph{D.~Hardesty~Lewis}, S.~A.~Pierce. "From \textsc{modflow}-96 to \textsc{modflow}-2005, \textsc{ParFlow}, and Others". {\small Poster presented at the 2017 annual fall meeting of the American Geophysical Union.}}
    \cvitem{2017~Dec.}{Kejriwal,~M., S.~A.~Pierce, P.~I.~Q.~Houser, S.~D.~Peckham, Z.~Stanko, \emph{D.~Hardesty~Lewis}. "Semi-automatic Data Integration using Karma". {\small Poster presented at the 2017 annual fall meeting of the American Geophysical Union.}}
    \cvitem{2016~July}{Cantu,~A., S.~A.~Pierce, O.~Rivera, A.~Ramirez, \emph{D.~Hardesty~Lewis}, J.~Gentle, G.~Fuentes-Pineda. "Big Data Analysis for Determining Sustainable Yield and Negotiation Space for an Aquifer System". {\small Poster presented at the 51\textsuperscript{st} annual meeting of the South-Central Section of the Geological Society of America.}}
    \cvitem{2016~Apr.}{\emph{Hardesty~Lewis,~D.} "On smoothness and Poisson's Equation". {\small Presented at the 2016 annual DRP Undergraduate Project Symposium at the University of Texas at Austin.}}
  \section{\textsc{Academic projects}}
    \cvitem{2022~June -- 2023~Aug.}{Advanced compound flood hazard assessment science  \newline{}
      {\small Partner with US Army Corps of Engineers to statistically model flood hazards in Texas's coastal region}}
    \cvitem{2021~Oct. -- 2023~Aug.}{Texas Disaster Information System (\textsc{TDIS})  \newline{}
      {\small Provide analytical web-based spatial data system to support more resilient decision-making at the state level}}
    \cvitem{2020~Dec. -- 2023~Aug.}{Museum of South Texas History Sunday Speaker Series  \newline{}
      {\small Provide Dash-enabled website to facilitate geolocation of archival imagery by museum visitors}}
    \cvitem{2020~Nov. -- 2023~Aug.}{Networks for Hazard Preparedness and Response  \newline{}
      {\small Overlay new, finely tuned flood maps over specially designed building and social vulnerability maps}}
    \cvitem{2020~Sep. -- 2023~Aug.}{Real-time flood inundation mapping to improve community resilience  \newline{}
      {\small Provide simple, computationally efficient, high-resolution flood inundation maps to emergency response personnel}}
    \cvitem{2020~Jan. -- 2023~Aug.}{Estimating Inundation Extent and Depth from National Water Model Outputs and High Resolution Topographic Data  \newline{}
      {\small Improving the accuracy of flood inundation estimation products from 10m to 1m resolution}}
    \cvitem{2017~Dec. -- 2023~Aug.}{MINT: Model INTegration Through Knowledge-Rich Data and Process Composition  \newline{}
      {\small Integrate geoscience models \textsc{modflow}, \textsc{hand}, \& \textsc{swat} with models from widely separate disciplines including agriculture, economics, and social sciences}}
    \cvitem{2016~Aug. -- 2023~Aug.}{Intelligent Systems for Geosciences  \newline{}
      {\small Used natural~language processing and ETL pipelines to capture geoscientific variables' metadata to integrate with intelligent systems}}
    \cvitem{2019~Sep. -- 2020~Aug.}{Improving the Estimation of Inundation Extent and Depth with High Resolution Terrain Data Over the State of Texas  \newline{}
      {\small Provided utilities to scale up the flood modelling toolset, GeoFlood, to statewide applicability across Texas}}
    \cvitem{2018~July -- 2019~Dec.}{Optimal Averaging of Water Resources in Texas  \newline{}
      {\small Indentified Texas water data sources, described their spatio-temporal scales and locations, estimated volume of all water in Texas its uncertainty, determined best methods to up-/down-scale all date to a common resolution and grid and minimise error}}
    \cvitem{2017~May -- 2017~Aug.}{From \textsc{modflow}-96 to \textsc{modflow}-2005, \textsc{ParFlow}, and Others  \newline{}
      {\small Brought a common groundwater flow model to scale on a supercomputer by updating its own Fortran code, using Perl natural~language processing to extract and transform useful metadata from its user manual, and helping to get that metadata incorporated into a widely used scientific ontology}}
    \cvitem{2016~July}{Big~Data Analysis for Determining Sustainable~Yield and Negotiation~Space for an Aquifer~System  \newline{}
      {\small Developed some Perl transformation routines between input file~formats of groundwater models, \textsc{modflow}-96 and \textsc{ParFlow}}}
    \cvitem{2014~Oct. -- 2014~Dec.}{Stochastic Differential~Equations and Monte~Carlo Simulation  \newline{}
      {\small Drafted Fortran routine that could run arbitrary equations of this type with arbitrary parameters}}
    \cvitem{2013~May -- 2013~Dec.}{Region of Calculated Existence for O/Ne-Core~Stars with H/He~Envelopes  \newline{}
	{\small Verified known observations, discovering that \textsc{mesa} accurately models this type of star under its default parameters}}%implemented particular parameters in \textsc{mesa} that confirmed that it simulates accurately these types of stars
  \section{\textsc{Professional projects}}
%%%    \cventry{2014~Sep. -- 2018 Aug.}{Maintenance \& technology officers}{Avalon\emph{, }Helios\emph{, then} Royal Co-operatives\emph{, }\textsc{icc}}{Austin,~United~States}{}{Redeveloped the internet infrastructures for these co-operative houses  \newline{}
    \cventry{2019~Nov. -- 2024~Dec.}{Board member}{Austin Community Reinvestment Cooperative (ACRC)}{Austin,~United~States}{}{Helped establish cooperative real estate investment firm  \leavevmode\newline{}
      Detailed accomplishments:
      \begin{itemize}
	\item {\small Shaped bylaws and business plan, having consulted with advisors who've had 40+ years in cooperative development experience}
	\item {\small Provide GIS maps of specific properties to follow for a potential purchase, having selected them from criteria applied across parcel-level data}
	\item {\small Provide heat maps to help determine the best neighborhoods for investment based on parcel-level zoning, existing building characteristics, and simple Python pro formas}
	\item {\small Develop fully detailed real estate development pro formas for specific properties}
	\item {\small Develop and maintain relationships with Central Austin property owners interested in a collaboration}
	\item {\small Develop and submit options-to-purchase to interested property owners}
      \end{itemize}}
%%%    \cventry{2019~Nov. -- Present}{Board member}{Austin Community Reinvestment Cooperative (ACRC)}{Austin,~United~States}{}{  \newline{}
    \cventry{2019~May -- Present}{Member-owner}{Hardy Cooperative}{Austin,~United~States}{}{Helped establish Central Austin affordable housing cooperative  \leavevmode\newline{}
      Detailed accomplishments:
      \begin{itemize}
	\item {\small Helped establish affordable housing cooperative of 7+ households in Central Austin, generating \$60,000+ in annual revenue while providing rents 35\% more affordable than nearby alternatives}
	\item {\small Collaborated with Dave Sullivan, former long-time chair of Austin planning commission, to determine that we met all zoning requirements for our use}
	\item {\small Secured 3 guarantors willing to front \$40,000-\$80,000 in liability for our commercial lease and new venture}
	\item {\small Drafted and implemented business prospectus, operational pro forma, resident lease applications, resident lease agreements, guarantor agreements, loan agreements, etc}
	\item {\small Maintained good relationships with 2 separate pro bono attorneys who have extensively reviewed, provided feedback, and largely rubber-stamped the contracts I have written}
	\item {\small Secured \$30,000+ in lending, as well as conditional approval for another \$40,000}
	\item {\small Received 150+ applicants for only 7 spaces in just 2 years of operation}
	\item {\small Established and maintained relationships with a 20+-year old housing coop and the ACRC in order to secure the long-term future of this venture}
      \end{itemize}}
%%%    \cventry{2019~May -- Present}{Member-owner}{Hardy Cooperative}{Austin,~United~States}{}{  \newline{}
    \cventry{2019~May -- 2020 Apr.}{Member, housing committee}{Austin Cooperative Business Association}{Austin,~United~States}{}{Austin Land Development Code (LDC) Revision  \leavevmode\newline{}
      Detailed accomplishments:
      \begin{itemize}
	\item {\small Reviewed cumulative 3000+ pages of 6 different Austin LDCs (1972, 1984, current, and LDC drafts 1, 2, \& 3)}
	\item {\small Developed ACBA policy positions from understanding of these codes}
	\item {\small Distributed GIS maps depicting impact of each proposed LDC draft and our proposed LDC amendments on current and future affordable housing cooperative development}
	\item {\small Secured meeting with Mayor Steve Adler}
	\item {\small Advocated ACBA's position in direct meetings with Mayor Steve Adler, CM Greg Casar, CM Harper-Madison's policy director, CM Leslie Pool's chief of staff, and City Staff LDC drafters}
	\item {\small Notified co-ops impacted by potential code changes and put them in touch with relevant City Council and City Staff members}
	\item {\small Helped advance ACBA positions through different City Councilmember offices and conducted vote-counts of each position before and after each vote}
	\item {\small Succeeded in getting amendments adopted into draft LDC}
      \end{itemize}}
  \section{\textsc{Review committees}}
    \cvitem{2023~Mar. -- 2023~Apr.}{Frontera Fellows applications  \newline{}
      {\small Helped TACC determine the most qualified doctoral fellows' projects on one of the largest supercomputers in the world}}
    \cvitem{2022 Aug.}{TACC's Frontera Pathways \& Large-Scale Community Partnerships applications  \newline{}
      {\small Helped approved/deny millions of dollars in computing resources to multimillion-dollar projects}}
  \section{\textsc{Students mentored}}
    \cvitem{2021~Aug. -- 2023~Aug.}{Khushboo Agarwal  \newline{}
      {\small MS Energy and Earth Resources, the University of Texas at Austin (expected 2023)}}
    \cvitem{2020~Aug. -- 2023~Aug.}{Mark Wang  \newline{}
      {\small PhD Civil Engineering, the University of Texas at Austin (expected 2025)}  \newline{}
      {\small MS Environmental and Water Resources Engineering, the University of Texas at Austin (2022)}}
    \cvitem{2019~Aug. -- 2021~May}{Robert Schomp  \newline{}
      {\small MS Environmental and Water Resources Engineering, the University of Texas at Austin (2021)}}
    \cvitem{2019~Aug. -- 2020~May}{Alec Carruthers  \newline{}
      {\small MS Environmental Engineering Technology / Environmental Technology, the University of Texas at Austin (2020)}}
  \section{\textsc{Pertinent coursework}}
    \cvlistitem{\emph{Mathematics} {\small Advanced~Calculus~for~Applications, Linear~Algebra~and~Matrix~Theory, Differential~Equations, Real~Analysis~I, Probability~I, Partial~Differential~Equations~and~Applications, Topology~I, Algebraic~Structures~I, Complex~Analysis, Vector~Calculus}}
    \cvlistitem{\emph{Scientific computing} {\small Introduction~to~Scientific~\&~Technical~Computing, Artificial~Intelligence~\emph{(audited)}, Mathematical~Modelling~in~Science~and~Engineering, Introduction~to~Stochastic~Processes, Applied~Statistics}}
    \cvlistitem{\emph{Political and social sciences} {\small \emph{(2019 ICPSR Summer Program, University of Michigan)} Intro~to~Network~Analysis, Machine~Learning, Math~for~Social~Sciences~III}}
  \section{\textsc{Professional~affiliations}}
    \cvlistitem{\emph{Mathematical Association of America} {\small Member}}
    \cvlistitem{\emph{North American Students of Cooperation} {\small Member}}
%%%		Member during 2013/07-Present
    \cvlistitem{\emph{American Geophysical Union} {\small Member}}
  \section{\textsc{Extracurricular~activities}}
    \cvlistitem{\emph{Austin Transportation Equity Analysis Zones Advisory Team} {\small Member, one of 30 members selected from a pool of 177 applicants to advise Austin Transportation on equitable geographic allocation of Project Connect's anti-displacement bond}}
%%%		Member during 2021/05-2021/07
    \cvlistitem{\emph{Austin Community Reinvestment Cooperative (ACRC)} {\small Board member}}
%%%		Member during 2019/11-Present
    \cvlistitem{\emph{Austin Cooperative Business Assocation (ACBA)} {\small Member, Development committee}}
%%%		Member during 2019/11-Present
    \cvlistitem{\emph{Evolve Austin} {\small Member, affiliate organization}}
%%%		Member during 2019/10-Present
    \cvlistitem{\emph{AURA} {\small Member}}
%%%		Member during 2019/10-Present
    \cvlistitem{\emph{Brentwood Neighborhood Association} {\small Member, provided PIR of full set of Affordability Unlocked applications}}
%%%		Member during 2019/08-Present
    \cvlistitem{\emph{Hardy Cooperative} {\small Founder, member-owner}}
%%%		Member during 2019/08-Present
    \cvlistitem{\emph{Austin Cooperative Business Assocation (ACBA)} {\small Member, Housing committee}}
%%%		Member during 2018/04-Present
    \cvlistitem{\emph{Mission~Interuniversitaire de Coordination~Échanges Franco-Américains} {\small Foreign~exchange}}
%%%		Member during 2016/08-2017/01
    \cvlistitem{\emph{Directed~Reading Program} {\small Graduate mathematical readings under individual guidance of doctoral~students}}
%%%     Mentee during XXXXXXXXXXXXXXX [Fill in.]
%%%		Mentee during 2016/01-2016/05
    \cvlistitem{\emph{Mathematics Club} {\small Attended student- and professor-led talks}}
%%%		Member during 2014/08-2016/05
    \cvlistitem{\emph{Inter-Cooperative Council (ICC) Austin} {\small Member}}
%%%		Member during 2014/01-2018/07
    \cvlistitem{\emph{College Houses Cooperatives} {\small Member}}
%%%		Member during 2013/07-2013/12
    \cvlistitem{\emph{Emerging~Scholars Program, Calculus} {\small Explored calculus outside of course~material}}
%%%		Member during 2012/08-2013/05
  \section{\textsc{Languages}}
    \cvdoubleitem{French}{Professional working}{Spanish}{Native}

\end{document}