\documentclass[letterpaper, 10pt,colorlinks,linkcolor=cyan]{moderncv}
  \usepackage{lmodern}
  \usepackage[english]{babel}
  \usepackage{courier}
  \hyphenpenalty=100000
  \hbadness=99999
%% Themes
  \moderncvstyle{casual}
  \moderncvcolor{red}
  \nopagenumbers{}

% --- Name in red (color1) while preserving casual's font weight split ---
  \colorlet{lastnamecolor}{color1}
  \colorlet{firstnamecolor}{color1}
  % Force section titles to red
  \colorlet{sectioncolor}{color1}
  \colorlet{subsectioncolor}{color1}
  % Force horizontal section bar to red
  \colorlet{bodyrulecolor}{color1}
  % Override section style to remove small caps and use upshape
  \renewcommand*{\sectionstyle}[1]{{\Large\bfseries\upshape\textcolor{sectioncolor}{#1}}}
  % Override subsection style to remove small caps
  \renewcommand*{\subsectionstyle}[1]{{\large\bfseries\upshape\textcolor{subsectioncolor}{#1}}}
  % Reduce body font to 9pt
  \renewcommand{\normalsize}{\fontsize{9}{11}\selectfont}
%% Encoding
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
%% Margins
  \usepackage[left=0.65in,right=0.65in,top=0.5in,bottom=1.0in]{geometry}
  \setlength{\hintscolumnwidth}{2.25cm}
%% Data
  \firstname{Daniel}
  \familyname{Hardesty Lewis}
  \address{\textsc{155~Claremont~Ave}}{\textsc{New~York,~NY~10027}}{\textsc{United~States}}
  \phone[mobile]{+1~(713)~371-7875}
  \email{daniel@summitgeospatial.com}
  \homepage{dlewis.ai}
  \social[linkedin]{dhardestylewis}
  \social[github]{dhardestylewis}

  \extrainfo{\href{https://scholar.google.com/citations?user=agBdssgAAAAJ}{Google Scholar}}
  \title{\large Staff ML Engineer -- production training, inference, evaluation, reliability}
%% Define \cvdoublecolumn
  \newcommand{\cvdoublecolumn}[2]{
    \cvitem[0.75em]{}{
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
      \hfill
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
  }

\begin{document}
  \definecolor{links}{HTML}{0645AD}
  \hypersetup{urlcolor=links}
  \vspace*{-2.5em}
  \makecvtitle

\vspace{-0.6em}
\noindent\begin{minipage}{\textwidth}
\small\raggedright
Specializing in automated validation frameworks and scalable distributed infrastructure. Delivered consumer pricing and statewide resiliency platforms across geospatial \& time-series workloads.
\end{minipage}
\vspace{0.6em}

  \section{Core Expertise}
  \cvitem{8 years}{\textbf{ML Engineering}: Build and operate AI/ML training and inference pipelines, with evaluation harnesses that catch regressions and improve production reliability}
  \cvitem{8~years}{\textbf{Backend \& Data}: Build schemas and ETL; ship API-backed services using Python, SQL, and Postgres/PostGIS}
  \cvitem{8~years}{\textbf{Distributed Systems}: Scale batch workloads across distributed systems, profile bottlenecks, and optimize latency \& throughput with explicit cost-performance tradeoffs}
  \cvitem{10~years}{\textbf{Geospatial AI}: Spatiotemporal modeling for risk, planning, and hazard decision-support use cases}
  \cvitem{8~years}{\textbf{Technical Leadership}: Drive cross-functional execution via specifications and governance; mentor engineers through design reviews, code reviews, and instruction}

  \section{Technologies}
  \cvitem{Modeling}{PyTorch; TensorFlow; scikit-learn; Hugging Face Transformers; LoRA/QLoRA/PEFT}
  \cvitem{LLM apps}{embeddings; RAG; LangChain; LangGraph; DSPy; FAISS}
  \cvitem{Data stack}{Python; SQL; Pandas; Polars; PyArrow; Parquet; Postgres; PostGIS; Redis; Elasticsearch; Supabase}
  \cvitem{Infrastructure}{Linux/Unix; Bash; Git; Docker; Kubernetes; Ray; Spark; Dask; Airflow; CI/CD; observability}
  \cvitem{Additional}{CUDA; C++; TypeScript; React}

  
  \section{\textsc{Experience}}
  \subsection{\textsc{Professional}}
    \cventry{Apr.~2025 -- Present}{Co-founder}{Properlytic}{New York, NY}{}{
    Building a consumer real-estate pricing product focused on individual home price forecasting.
    \begin{itemize}
        \item Deployed a current-price prediction model for Manhattan condos and co-ops; achieved 12\% MAPE on a holdout set and matched Zillow at 8.4\% MAPE under an internal apples-to-apples evaluation protocol.
        \item Architected a VAE-based latent representation model over property, transaction, and neighborhood attributes to stabilize learning and improve generalization under sparse and noisy features.
        \item Prototyped a \href{https://houston-price-prediction.vercel.app/}{diffusion-based forecasting backbone in Houston}; measured 8\% annualized compounding error even through regime shifts such as COVID.
        \item Migrated market-specific models onto the diffusion backbone for standardized training and evaluation.
        \item Refined product positioning and execution milestones via strategic feedback from a16z, MetaProp, and others.
        \item Pitch deck: \href{https://docs.google.com/presentation/d/1HL2zPTLxuGdq9k12Z6J_RQA4Dt64ZKEsSVrTQpbQuNA/edit?usp=sharing}{link}
    \end{itemize}}

    \cventry{Nov.~2024 -- Present}{Co-founder}{\href{https://www.polibom.com/}{PoliBOM}}{Seattle, WA}{}{
    AI tariff mitigation and trade compliance product for manufacturers, centered on BOM analysis, retrieval, and policy scenario simulation
    \begin{itemize}
      \item Specified an agentic workflow and schema definitions for BOM parsing, retrieval, and tariff simulation using Airflow, Elasticsearch and embeddings, and FastAPI serving backed by Supabase and Redis.
      \item Engineered a what-if framework to analyze BOM cost impacts, lead times, and compliance risks.
      \item Executing customer discovery with global importers/exporters to iterate on distribution and compliance pricing models.
      \item Secured market validation by presenting the prototype to KPMG, pre-dating their subsequent launch of a \href{https://kpmg.com/xx/en/home/insights/2024/05/tariff-modeler.html}{commercial tariff-modeling product}.
    \end{itemize}}

    \cventry{Nov.~2023 -- Present}{Founder}{\href{https://summitgeospatial.com}{Summit Geospatial}}{New York, NY}{}{
    High-resolution elevation data and web delivery for engineering and hazard workflows.
    \begin{itemize}
      \item Engineered a 0.5~m statewide seamless Texas DEM mosaic using nearest-neighbor stitching across 70+ state, federal, and local elevation sources.
      \item Developed the web distribution platform end-to-end including data pipeline, tiling, hosting, delivery UX to support engineering and planning use cases.
      \item Commercial discussions to license elevation datasets to research and AI organizations.
    \end{itemize}}

    \cventry{Aug.~2021 -- Aug.~2023}{Senior Data Scientist \& Technical Lead}{\href{https://www.tacc.utexas.edu/}{Texas Advanced Computing Center (TACC)}}{Austin, TX}{}{
    \begin{itemize}
        \item Co-founded and launched \href{https://www.summitgeospatial.com}{summitgeospatial.com} to commercialize state-level geomorphology IP, providing precision decision-support for civil engineering and disaster planning.
        \item Led the source-to-frontend data pipeline for the \$40M \href{https://idrt.tamug.edu/tdis/}{Texas Disaster Information System (TDIS)}, integrating large-scale geospatial assets for state-level resiliency.
        \item Led inter-agency RFP and MOU development with state and federal partners incl. USACE, Texas GLO, translating technical requirements into scope and milestones enabling the \$40M resiliency platform.
        \item Scaled climate and flood models on supercomputers, executing million-node distributed jobs while managing multi-million-dollar compute budgets and federal partnerships with NOAA, NSF, USCE, GLO.
        \item Partnered with the US Army Corps of Engineers to statistically model compound flood hazards in coastal Texas, integrating high-resolution topographic data with hydrological models.
        \item Developed efficient methods to produce high-resolution (1m) flood maps from National Water Model outputs for Texas Emergency Management's \href{https://storymaps.arcgis.com/stories/6227f24d6c5047f883d5c3497241f299}{Real-Time Inundation Mapping}.
        \item Contributed fundamental research supporting Paola Passalacqua's 2022 EGU Bagnold Medal, one of geomorphology's highest honors.
    \end{itemize}}
    
    \cventry{Feb.~2018 -- Jul.~2021}{Data Scientist \& Research Engineer}{\href{https://www.tacc.utexas.edu/}{Texas Advanced Computing Center (TACC)}}{Austin, TX}{}{
    \begin{itemize}
        \item Competed in \href{https://www.darpa.mil/program/world-modelers}{DARPA World Modelers} to improve disaster resiliency and food security modeling in East Africa.
        \item Mentored Petrobras engineers in deep learning and HPC to enable institutional technology transfer.
        \item Received research recognition from AAAI President Yolanda Gil during her \href{https://youtu.be/3Spk_UOHNxA?t=2377}{farewell address} for contributions to automated scientific modeling.
    \end{itemize}}


  \subsection{\textsc{Research}}

    \cventry{May~2025 -- Present}{Research assistant to Dir. Electrical Engineering Zoran Kostic}{Columbia University}{New York, NY}{}{
    \begin{itemize}
        \item Math benchmarking and finetuning of Deepseek's GRPO algorithm
    \end{itemize}}

    \cventry{Jan.~2025 -- Present}{Research assistant to Dir. Financial Engineering Ali Hirsa}{Columbia University}{New York, NY}{}{
    \begin{itemize}
        \item Developed a multi-asset conditional variational autoencoder (CVAE) latent factor model with Skew-T Mixture priors; achieved 85\% \(R^2\) vs.\ commercial SaaS (75\%) and Fama-French (58\%) on backtested holdout.
        \item Derived a tractable, axiom-compliant per-feature SHAP algorithm using Hessian-based recursive clustering to provide stable temporal regime-dependent attributions for deep learning models.
    \end{itemize}}
    
    \cventry{July~2019 -- Aug.~2019}{Summer research intern to Pres. AAAI Yolanda Gil}{University of Southern California}{Los Angeles, CA}{}{
    \begin{itemize}
        \item Integrated hydrological models into the \href{http://mint-project.info/overview.html}{MINT Platform} during a year-long competition with MITRE to provide DARPA the "Airflow for science"
    \end{itemize}}

  \subsection{\textsc{Teaching}}
    \cventry{Jan.~2018 -- Dec.~2020}{Co-instructor}{The University of Texas at Austin}{Austin, TX}{}{
    \begin{itemize}
        \item Helped teach graduate-level courses: \emph{Machine Learning for the Geosciences} for Petrobras engineers, \emph{Intelligent Systems for the Geosciences}, and \emph{Scientific Computation}, including C++, CUDA, HPC, \& optimization.
    \end{itemize}}

  \section{\textsc{Select Publications}}
    \cvitem{2021}{Gil, Y., et al. (incl. \textbf{D. Hardesty Lewis}), ``Artificial Intelligence for Modeling Complex Systems: Taming the Complexity of Expert Models to Improve Decision Making''. \emph{ACM TiiS}, 2021. DOI: \href{https://doi.org/10.1145/3453172}{10.1145/3453172}}
    \cvitem{2019}{Garijo, D., et al. (incl. \textbf{D. Hardesty Lewis}), ``An intelligent interface for integrating climate, hydrology, agriculture, and socioeconomic models''. \emph{ACM IUI '19}, 2019. DOI: \href{https://doi.org/10.1145/3308557.3308711}{10.1145/3308557.3308711}}

  \section{\textsc{Education}}
    \cventry{expected 2026}{M.S., Urban Planning}{Columbia University}{New York City,~NY}{}{}
    \cventry{2017}{B.S., Pure Mathematics}{University of Texas}{Austin,~TX}{}{}
    \cventry{2017}{Certificate, Scientific~Computation}{University of Texas}{Austin,~TX}{}{}

  \section{\textsc{Key Projects}}

    \cvitem{oppsAlert}{Developed the first property- and owner-level ML model of NIMBYism, using 15+ years of 15,000+ points of individual homeowner protest data provided by the City of Austin.}





  \section{\textsc{Activities}}
    \cvdoubleitem{Sailing}{Volunteer Atlantic SAR of the \href{https://en.wikipedia.org/wiki/Cheeki_Rafiki}{Cheeki Rafiki}}{Bikepacking}{US West \& East Coasts}

  \section{\textsc{Languages}}
    \cvdoubleitem{Spanish}{Native Proficiency}{French}{Professional Working Proficiency}

\end{document}
