\documentclass[letterpaper, 10pt,colorlinks,linkcolor=cyan]{moderncv}
  \usepackage{lmodern}
  \usepackage[english]{babel}
  \usepackage{courier}
  \hyphenpenalty=100000
  \hbadness=99999
%% Themes
  \moderncvstyle{casual}
  \moderncvcolor{red}
  \nopagenumbers{}
%% Encoding
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
%% Margins
  \usepackage[scale=0.85]{geometry}
  \setlength{\hintscolumnwidth}{2.81cm}
%% Data
  \firstname{\textsc{Daniel}}
  \familyname{\textsc{Hardesty Lewis}}
  \address{\textsc{155~Claremont~Ave}}{\textsc{New~York,~NY~10027}}{\textsc{United~States}}
  \phone[mobile]{+1~(713)~371-7875}
  \email{daniel@homecastr.com}
  % \homepage{tacc.utexas.edu/about/directory/daniel-lewis}
  \social[linkedin]{dhardestylewis}
  \social[github]{dhardestylewis}
  \social[gitlab]{dhl}
  \extrainfo{\url{researchgate.net/profile/Daniel-Hardesty-Lewis}}
%% Define \cvdoublecolumn
  \newcommand{\cvdoublecolumn}[2]{
    \cvitem[0.75em]{}{
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
      \hfill
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
  }

\begin{document}
  \definecolor{links}{HTML}{0645AD}
  \hypersetup{urlcolor=links}
  \makecvtitle


  \section{\textsc{Experience}}
  \subsection{\textsc{Professional}}
    \cventry{Apr. 2025 -- Present}{Co-founder}{Homecastr}{New York, NY}{}{
    Building a consumer real-estate pricing product focused on individual home price forecasting.
    \begin{itemize}
        \item Deployed a current-price prediction model for Manhattan condos and co-ops; achieved 12\% MAPE on a holdout set and matched Zillow at 8.4\% MAPE under an internal apples-to-apples evaluation protocol.
        \item Built a VAE-based latent representation layer over property, transaction, and neighborhood signals to stabilize learning and improve generalization under sparse and noisy features.
        \item Prototyped a diffusion-based forecasting backbone in Houston; measured 8\% annualized compounding error on backtests spanning the 2020–2021 COVID period.
        \item Migrating market-specific models onto the diffusion backbone to standardize training, calibration, and evaluation across markets.
        \item Conducted investor discussions with a16z, MetaProp, and other firms; incorporated feedback into product positioning and milestones.
        \item Pitch deck: \href{https://docs.google.com/presentation/d/1HL2zPTLxuGdq9k12Z6J_RQA4Dt64ZKEsSVrTQpbQuNA/edit?usp=sharing}{link}
    \end{itemize}}

    \cventry{Nov. 2024 -- Present}{Co-founder}{PoliBOM}{Seattle, WA}{}{
    AI tariff mitigation and trade compliance product for manufacturers, centered on BOM analysis, retrieval, and policy scenario simulation
    \begin{itemize}
      \item Specified an agentic workflow and data contracts for BOM parsing, retrieval, and tariff simulation using Airflow, Elasticsearch and embeddings, Pydantic-validated JSON interfaces, and FastAPI serving backed by Supabase and Redis
      \item Built the tariff simulation and what-if framework for policy scenarios affecting BOM cost, lead times, and compliance risk, including China decoupling and Section 301 exposure analysis
      \item Presented the prototype to enterprise stakeholders including KPMG; market validation: KPMG subsequently launched a tariff-modeling product (\href{https://kpmg.com/us/en/capabilities-services/tax-services/international-tax-trade-and-transfer-pricing/trade-customs/kpmg-tariff-modeler.html}{link})
      \item Raising seed; running customer discovery with importers and exporters and iterating on distribution, pricing, and compliance workflows
    \end{itemize}}

    \cventry{Nov. 2023 -- Present}{Founder}{Summit Geospatial}{New York, NY}{}{
    High-resolution elevation data and web delivery for engineering and hazard workflows (\href{https://summitgeospatial.com}{summitgeospatial.com}).
    \begin{itemize}
      \item Built a 0.5 m statewide seamless Texas DEM mosaic using nearest-neighbor stitching across 70+ state, federal, and local elevation sources.
      \item Built the web distribution platform end-to-end (data pipeline, tiling, hosting, delivery UX) to support engineering and planning use cases.
      \item Commercial discussions to license elevation datasets to research and AI organizations.
    \end{itemize}}

    \cventry{Aug. 2021 -- Aug. 2023}{Senior Data Scientist \& Technical Lead}{Texas Advanced Computing Center (TACC)}{Austin, TX}{}{
    \begin{itemize}
        \item Spun out Summit Geospatial alongside UT's VPs of IP
        \item Led source-to-frontend data pipeline for \$40M Texas Disaster Information System (TDIS) disaster resiliency initiative
        \item Delivered \href{https://www.summitgeospatial.com}{summitgeospatial.com}, a precision decision-support platform used by civil engineers to quantify risk and allocate resources for disaster planning
        \item Contributed research towards Paola Passalacqua's 2022 EGU Bagnold Medal, one of geomorphology's highest honors
        \item Scaled climate and flood models on world-leading supercomputers, utilizing millions of dollars in computational resources and million-node jobs
        \item Evaluated and accepted tens of millions of dollars in compute requests
        \item Managed relationships and developed projects with federal, state agencies, and universities including NOAA, NSF, US Army Corps of Engineers, Texas General Land Office, USC, UT, A\&M
    \end{itemize}}
    
    \cventry{Feb. 2018 -- Jul. 2021}{Data Scientist \& Research Engineer}{Texas Advanced Computing Center (TACC)}{Austin, TX}{}{
    \begin{itemize}
        \item Competed in DARPA World Modelers program, focusing on disaster resiliency in East Africa
        \item Research received a mention from President of AAAI Yolanda Gil during her farewell speech
        \item Helped teach Petrobras deep learning on HPC
    \end{itemize}}

  \subsection{\textsc{Research}}

    \cventry{May 2025 -- Present}{Research assistant to Dir. Electrical Engineering Zoran Kostic}{Columbia University}{New York, NY}{}{Targetting theory publications to DeepSeek's GRPO algorithm}

    \cventry{Jan. 2025 -- Present}{Research assistant to Dir. Financial Engineering Ali Hirsa}{Columbia University}{New York, NY}{}{Achieved better than  \href{https://www.arcana.io/}{commercial \(R^2\)} on backtested holdout prediction of daily mutual fund returns on a variety of asset classes
    \begin{itemize}
        \item Using a DL latent factor model to produce better factors than our benchmark: Fama-French's 5-factor model
        \item Now targetting SHAP explainability publication
    \end{itemize}}
    
    \cventry{July 2019 -- Aug. 2019}{Summer research intern to Pres. AAAI Yolanda Gil}{University of Southern California}{Los Angeles, CA}{}{Integrated hydrological models into team's DARPA-supported scientific model orchestration portal}

  \subsection{\textsc{Teaching}}

    \cventry{Jan. 2018 -- Dec. 2020}{Co-instructor}{The University of Texas at Austin}{Austin, TX}{}{Helped teach graduate-level courses: \emph{Machine Learning for the Geosciences}, \emph{Intelligent Systems for the Geosciences}, and \emph{Scientific Computation}, including C++, CUDA, HPC, \& optimization}

  \section{\textsc{Education}}
    \cventry{expected 2026}{M.S., Urban Planning}{Columbia University}{New York City,~NY}{}{}
    \cventry{2017}{B.S., Pure Mathematics}{University of Texas}{Austin,~TX}{}{}
    \cventry{2017}{Certificate, Scientific~Computation}{University of Texas}{Austin,~TX}{}{}

  \section{\textsc{Key Projects}}
    \cvitem{oppsAlert}{Developed the first property- and owner-level ML model of NIMBYism, using 15+ years of 15000+ points of individual homeowner protest data provided by the City of Austin}
    \cvitem{Stealth, RegTech}{\textit{Seeking PE investment:} Teaming up with a top-proptech operator for a very large opportunity to aid cities achieve permitting compliance via simple pipeline collating publicly available imagery against permitting data}
    \cvitem{Flood Hazard Assessment}{Partnered with the US Army Corps of Engineers to statistically model compound flood hazards in coastal Texas, integrating high-resolution topographic data with hydrological models.}
    \cvitem{Texas Disaster Information System (\textsc{TDIS})}{Led development of the core elevation data layer for a web-based spatial data system that supports resilient decision-making at the state and local levels.}
    \cvitem{Real-Time Inundation Mapping}{Developed computationally efficient methods to produce high-resolution (1m) flood inundation maps from National Water Model outputs for emergency response personnel.}

  \section{\textsc{Technology Skills}}
    \cvdoubleitem{Programming Languages}{\raggedright Python, Bash, PL/pgSQL, Fortran, Perl, C++}{Operating Systems}{\raggedright \textsc{gnu}/Linux, mac\textsc{os}, Windows}
    \cvdoubleitem{Libraries \& Frameworks}{\raggedright \textsc{gdal}, \textsc{cuda}, GeoPandas, RasterIO, NumPy, Plotly, Dash}{Database Systems}{\raggedright PostgreSQL, Redis, Supabase, PostGIS}
    \cvdoubleitem{Scientific Software}{\raggedright \textsc{modflow}, \textsc{hand}, \textsc{hec-ras}, \textsc{mesa}}{Cloud \& Virtualization}{\raggedright AWS, Azure, Docker, Singularity}
    \cvdoubleitem{AI tooling}{\raggedright ChatGPT, Claude, Gemini, VSCode, v0.dev}{ML}{\raggedright \textsc{vae}, Tree-based models}
    \cvdoubleitem{Clustering techniques \& metrics}{\raggedright \textsc{dbscan}, Hierarchical, Silhouette score, Calinski-Harabasz, Davies-Bouldin}{Statistical \& ML metrics}{\raggedright 
     \(R^2\), \textsc{mape}, \textsc{rmse}, KL-div, Reconstruction loss}

  \section{\textsc{Languages}}
    \cvdoubleitem{Spanish}{Native / Bilingual Proficiency}{French}{Professional Working Proficiency}

\end{document}