\documentclass[letterpaper, 10pt,colorlinks,linkcolor=cyan]{moderncv}
  \usepackage{lmodern}
  \usepackage[english]{babel}
  \usepackage{courier}
  \hyphenpenalty=100000
  \hbadness=99999
%% Themes
  \moderncvstyle{casual}
  \moderncvcolor{red}
  \nopagenumbers{}

% --- Name in red (color1) while preserving casual's font weight split ---
  \colorlet{lastnamecolor}{color1}
  \colorlet{firstnamecolor}{color1}
  % Force section titles to red
  \colorlet{sectioncolor}{color1}
  \colorlet{subsectioncolor}{color1}
  % Force horizontal section bar to red
  \colorlet{bodyrulecolor}{color1}
  % Override section style to remove small caps and use upshape
  \renewcommand*{\sectionstyle}[1]{{\Large\bfseries\upshape\textcolor{sectioncolor}{#1}}}
  % Override subsection style to remove small caps
  \renewcommand*{\subsectionstyle}[1]{{\large\bfseries\upshape\textcolor{subsectioncolor}{#1}}}
  % Reduce body font to 9pt
  \renewcommand{\normalsize}{\fontsize{9}{11}\selectfont}
%% Encoding
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
%% Margins
  \usepackage[left=0.65in,right=0.65in,top=0.5in,bottom=1.0in]{geometry}
  \setlength{\hintscolumnwidth}{2.25cm}
%% Data
  \firstname{Daniel}
  \familyname{Hardesty Lewis}
  \address{\textsc{500~Riverside~Dr}}{\textsc{New~York,~NY~10027}}{\textsc{United~States}}
  \phone[mobile]{+1~(713)~371-7875}
  \email{daniel@summitgeospatial.com}
  \homepage{dlewis.ai}
  \social[linkedin]{dhardestylewis}
  \social[github]{dhardestylewis}

  \extrainfo{\href{https://scholar.google.com/citations?user=agBdssgAAAAJ}{Google Scholar}}
  \title{\large Forward Deployed Engineer -- full-stack, enterprise operations, AI \& automation}
%% Define \cvdoublecolumn
  \newcommand{\cvdoublecolumn}[2]{
    \cvitem[0.75em]{}{
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
      \hfill
      \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
  }

\begin{document}
  \definecolor{links}{HTML}{0645AD}
  \hypersetup{urlcolor=links}
  \vspace*{-2.5em}
  \makecvtitle

\vspace{-0.6em}
\noindent\begin{minipage}{\textwidth}
\small\raggedright
Engineer and founder specializing in bridging product engineering and enterprise stakeholders. Built full-stack platforms, automated operational workflows, and shipped customer-facing tooling from scoping through launch.
\end{minipage}
\vspace{0.6em}

  \section{Core Expertise}
  \cvitem{8 years}{\textbf{Full-Stack Engineering}: Ship production web applications end-to-end using Python, React, SQL, and Postgres; own from data pipeline through user-facing delivery}
  \cvitem{4~years}{\textbf{Client Engineering \& Onboarding}: Triage enterprise requests, scope integrations, and own technical onboarding from kickoff through launch}
  \cvitem{8~years}{\textbf{Process Automation}: Find manual bottlenecks and replace them with automated workflows and AI tooling; build repeatable playbooks for client engagement}
  \cvitem{8~years}{\textbf{Communication \& Education}: Teach customers how to integrate, keep stakeholders current on project status, and document institutional knowledge}
  \cvitem{8~years}{\textbf{Technical Leadership}: Bridge engineering and stakeholders; mentor engineers through design reviews, code reviews, and hands-on instruction}

  \section{Technologies}
  \cvitem{Core stack}{Python; SQL; TypeScript; React; Postgres; Redis; Elasticsearch; Supabase; FastAPI}
  \cvitem{AI/ML}{LangChain; LangGraph; DSPy; RAG; FAISS; PyTorch; scikit-learn; Airflow}
  \cvitem{Data}{Pandas; Polars; PyArrow; Parquet; BigQuery; PostGIS; ETL pipelines}
  \cvitem{Infrastructure}{Linux; Git; Docker; Kubernetes; Terraform; CI/CD; monitoring \& observability}
  \cvitem{Additional}{CUDA; C++; Ray; Dask; Spark}

  
  \section{\textsc{Experience}}
  \subsection{\textsc{Professional}}
    \cventry{Apr.~2025 -- Present}{Co-founder}{\href{https://www.homecastr.com/}{Homecastr}}{New York, NY}{}{
    Real-estate pricing and forecasting platform built end-to-end with React, Python/FastAPI, and Postgres.
    \begin{itemize}
        \item Deployed a semi-supervised VAE on property records; achieved 12\% holdout error against Zillow's 8.4\% Zestimate.
        \item Shipped a diffusion-based forecasting system with fan charts; achieved 14\% annual compounding forecast error in production.
        \item Ran customer discovery and user interviews with a16z, MetaProp, SFR operators, and RE investors to scope requirements and sharpen product direction.
    \end{itemize}}

    \cventry{Nov.~2024 -- Present}{Co-founder}{\href{https://www.polibom.com/}{PoliBOM}}{Seattle, WA}{}{
    AI tariff mitigation product for manufacturers, centered on BOM analysis, retrieval, and policy scenario simulation; led \textbf{customer-facing scoping, demos, and technical onboarding} for enterprise prospects.
    \begin{itemize}
      \item Specified an \textbf{agentic workflow} and schema definitions for BOM parsing, retrieval, and tariff simulation.
      \item Directed a \textbf{conversational AI interface} enabling non-technical decision-makers to retrieve BOMs and receive proactive compliance alerts without engineering support.
      \item Ran \textbf{customer discovery and live demos} with Deloitte, ScoutyAI, and other import/export founders; \textbf{scoped integration requirements} for enterprise prospects.
      \item Contributed to materials presented to KPMG, pre-dating their launch of a \href{https://kpmg.com/xx/en/home/insights/2024/05/tariff-modeler.html}{tariff-modeling product}. Ongoing discovery with an ex-Goldman Sachs co-CIO and Columbia Business School tariff economists.
    \end{itemize}}

    \cventry{Nov.~2023 -- Present}{Founder}{\href{https://summitgeospatial.com}{Summit Geospatial}}{New York, NY}{}{
    The highest quality seamless elevation data for Texas; web delivery for engineering and hazard workflows.
    \begin{itemize}
      \item Engineered a statewide seamless Texas DEM mosaic, resampling 0.5~m LiDAR sources to 1.2~m via nearest-neighbor across 70+ state, federal, and local elevation datasets.
      \item Built the \textbf{web distribution platform end-to-end}: data pipeline, tiling, hosting, and delivery UX.
      \item Commercial discussions to license elevation datasets to research and AI organizations.
    \end{itemize}}

    \cventry{Aug.~2021 -- Aug.~2023}{Senior Data Scientist \& Technical Lead}{\href{https://www.tacc.utexas.edu/}{Texas Advanced Computing Center (TACC)}}{Austin, TX}{}{
    \begin{itemize}
        \item \textbf{Triaged and scoped enterprise requests} across 6+ state and federal agencies including NOAA, NSF, USACE, and GLO, translating requirements into SOW and MOU frameworks.
        \item Served as a primary \textbf{technical point of contact} for the \$40M \href{https://tdis.io/}{Texas Disaster Information System (TDIS)}, coordinating between engineering, Texas Emergency Management, and first responders.
        \item Documented data onboarding so partner agencies could \textbf{self-serve integrations} without engineering support.
        \item Managed \$1M+ compute allocations across 10+ projects, orchestrating 800,000-node distributed workloads on leadership-class supercomputers for climate and flood modeling.
        \item Spun out \href{https://www.summitgeospatial.com}{Summit Geospatial} alongside UT's VPs of IP to commercialize the platform's elevation data layer.
        \item \textbf{Evaluated and accepted} \$10M+ in computing resource requests as Technical Reviewer for \href{https://frontera-portal.tacc.utexas.edu/fellowship/}{Frontera Doctoral Fellows} and \href{https://frontera-portal.tacc.utexas.edu/allocations/pathways-awardees/}{Large-Scale Computing Pathways}, triaging proposals against capacity and impact criteria.
    \end{itemize}}
    
    \cventry{Feb.~2018 -- Jul.~2021}{Data Scientist \& Research Engineer}{\href{https://www.tacc.utexas.edu/}{Texas Advanced Computing Center (TACC)}}{Austin, TX}{}{
    \begin{itemize}
        \item Competed in year-long \href{https://www.darpa.mil/program/world-modelers}{DARPA World Modelers} program to improve disaster resiliency and food security modeling in East Africa, coordinating across distributed engineering and research teams.
        \item Received recognition from AAAI President Yolanda Gil during her \href{https://youtu.be/3Spk_UOHNxA?t=2377}{farewell address} for contributions to automated scientific modeling.
    \end{itemize}}


  \subsection{\textsc{Research}}
    \cventry{Jan.~2025 -- Oct.~2025}{Industry-sponsored research assistant to Ask2.AI CSO Ali Hirsa}{Columbia University}{New York, NY}{}{
    \begin{itemize}
        \item Developed a multi-asset CVAE latent factor model for \textbf{tabular financial data} with Skew-T Mixture priors; achieved 85\% \(R^2\) vs.\ commercial SaaS (75\%) and Fama-French (58\%) on backtested holdout.
        \item Derived a tractable, axiom-compliant per-feature SHAP algorithm using Hessian-based recursive clustering to provide stable temporal regime-dependent attributions for deep learning models.
    \end{itemize}}

    \cventry{May~2025 -- Aug.~2025}{Research assistant to Dir. Electrical Engineering Zoran Kostic}{Columbia University}{New York, NY}{}{Math benchmarking and finetuning of Deepseek's GRPO algorithm.}

    \cventry{July~2019 -- Aug.~2019}{Summer research intern to Pres. AAAI Yolanda Gil}{University of Southern California}{Los Angeles, CA}{}{Integrated hydrological models into \href{http://mint-project.info/overview.html}{MINT}'s scientific orchestration platform submission to DARPA.}

  \subsection{\textsc{Teaching}}
    \cventry{Jan.~2018 -- Dec.~2020}{Co-instructor}{The University of Texas at Austin}{Austin, TX}{}{
    \begin{itemize}
        \item Helped design and teach graduate-level courses: \emph{Machine Learning for the Geosciences} for Petrobras geoscientists and petroleum engineers, \emph{Intelligent Systems for the Geosciences}, and \emph{Scientific Computation}, including C++, CUDA, and HPC.
    \end{itemize}}

  \section{\textsc{Select Publications}}
    \cvitem{2021}{Gil, Y., et al. (incl. \textbf{D. Hardesty Lewis}), ``Artificial Intelligence for Modeling Complex Systems: Taming the Complexity of Expert Models to Improve Decision Making''. \emph{ACM TiiS}, 2021. DOI: \href{https://doi.org/10.1145/3453172}{10.1145/3453172}}
    \cvitem{2019}{Garijo, D., et al. (incl. \textbf{D. Hardesty Lewis}), ``An intelligent interface for integrating climate, hydrology, agriculture, and socioeconomic models''. \emph{ACM IUI '19}, 2019. DOI: \href{https://doi.org/10.1145/3308557.3308711}{10.1145/3308557.3308711}}

  \section{\textsc{Education}}
    \cventry{expected 2026}{M.S., Urban Planning}{Columbia University}{New York City,~NY}{}{}
    \cventry{2017}{B.S., Pure Mathematics}{University of Texas}{Austin,~TX}{}{}
    \cventry{2017}{Certificate, Scientific~Computation}{University of Texas}{Austin,~TX}{}{}

  \section{\textsc{Key Projects}}

    \cvitem{oppsAlert}{Developed the first property- and owner-level ML model of NIMBYism, comparing diffusion against logistic regression, using 15+ years of 15,000+ homeowner protest records from the City of Austin.}


  \section{\textsc{Activities}}
    \cvdoubleitem{Sailing}{Volunteer Atlantic SAR of the \href{https://en.wikipedia.org/wiki/Cheeki_Rafiki}{Cheeki Rafiki}}{Bikepacking}{US West \& East Coasts}

  \section{\textsc{Languages}}
    \cvdoubleitem{Spanish}{Native Proficiency}{French}{Professional Proficiency}

\end{document}
